\documentclass[12pt]{article}

\pagestyle{empty}
\usepackage[dvips,letterpaper,lmargin=0.9in,rmargin=0.9in,tmargin=0.9in,bmargin=0.9in]{geometry}
\usepackage{hyperref}
\usepackage{url}
\usepackage{fancyvrb}
\usepackage{titlesec}
\usepackage{verbatim}
\usepackage{nth}
\usepackage{textcomp}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\setlength{\parindent}{0pt}
\setlength{\parskip}{.3em plus0.1em minus0.1em}
\usepackage{enumitem}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
}

\makeatletter
\DeclareRobustCommand{\Cpp}
{\valign{\vfil\hbox{##}\vfil\cr
   {C\kern-.05em}\cr
   $\hbox{\fontsize{\sf@size}{0}\textbf{+\kern-0.05em+}}$\cr}%
}
\makeatother

\makeatletter
\DeclareRobustCommand{\Csharp}
{\valign{\vfil\hbox{##}\vfil\cr
   {C\kern .03em}\cr
   $\hbox{\fontsize{\sf@size}{0}\textbf{\#}}$\cr}%
}
\makeatother

\titlespacing{\paragraph}{0pt}{.5\baselineskip}{1em}
\titlespacing{\section}{0pt}{.5em}{.05em}
\titlespacing{\subsection}{0pt}{.5em}{.1em}
\setlength{\parskip}{0.5em}

\begin{document}
\begin{minipage}{0.65\textwidth}
I'm a SWE and eng leader specializing in making GPUs run fast.  I've led and
helped write most of Google's ML compilers stack, in clang, LLVM, and XLA.
I'm looking for the equivalent of a Google L7 role.
\end{minipage}
%
\hfill\begin{minipage}{0.30\textwidth}
\vspace{-1.40em}
\raggedleft
\framebox[2.00in][l]{\parbox[t]{1.80in}{
\raggedleft
\textbf{Justin Lebar}\\
\hfill justin.lebar@gmail.com \\ \vspace{0.5em}
\textit{Updated 2023 Aug}
}}
\end{minipage}

\section*{Timeline}

\begin{minipage}{7em} \textbf{2020--present} \end{minipage} Waymo tech lead and
  manager focused on GPU infra and performance.  I have impact across Waymo,
  ranging from strategic leadership to individual technical contributions.

\begin{itemize}[topsep=0em, itemsep=0pt, parsep=0.25em]
\item I set Waymo's GPU software strategy, e.g.\ deciding which compilers we use
  and which optimization opportunities (quantization, distillation, Triton,
  etc.) we focus on.
\item I've built a team of 5 formal and about 5 informal members.  We:
  \begin{itemize}[topsep=0em, itemsep=0pt, parsep=0em]
    \item own Waymo's LiDAR processing pipeline (written in CUDA),
    \item build infra for programming in CUDA (has cool portability and safety features), and
    \item build ML optimization infra (e.g.\ XLA and quantized-aware training).
  \end{itemize}
\item I'm involved in most ML model launches across the company, debugging
  latency issues and often fixing issues in XLA.
\item I'm the customer for the GPU part of Waymo's planned custom hardware.
  For example I defined the GPU's programming model.
\item I act as a tech lead and senior SWE for the Google XLA project.  I write
  and review code for XLA, clang, and LLVM and help grow the SWEs and TLs on
  the team.
\item I'm a \Cpp\ expert; I teach a class at Waymo, and I'm one of the top 10
  \Cpp\ readability reviewers by volume across all of Alphabet.
\end{itemize}

\begin{minipage}{5.5em} \textbf{Fall 2019} \end{minipage}
\href{https://buildyourfuture.withgoogle.com/programs/googleinresidence}{Taught}
a semester of intro CS at Hampton University.

\begin{minipage}{5.5em} \textbf{2016--2019} \end{minipage}
Google tech lead and manager for GPU compilers and XLA:CPU/GPU.

\begin{itemize}[topsep=0.25em, itemsep=0pt, partopsep=0pt]
\item I was part of the team of two that added support for CUDA in clang and
  made LLVM's PTX support usable.

\item Later I moved to working on XLA, where I led the XLA:CPU and XLA:GPU
  projects as the tech lead and one of the managers. During this time we
  transformed XLA from a toy into a product with real users.
\end{itemize}

\begin{minipage}{5.5em} \textbf{2013--2016} \end{minipage}
Google SWE on Census, a performance-monitoring and debugging tool.

\begin{minipage}{5.5em} \textbf{2011--2013} \end{minipage}
Gecko hacker at Mozilla.  I worked on many aspects of the platform --- I was an
official reviewer of seven modules.  I specialized in optimizing the browser's
memory usage.

\begin{minipage}{5.5em} \textbf{2006--2011} \end{minipage}
Stanford University, BS/MS in Computer Science.

\section*{Etc.}
\textbf{I'm good at} \Cpp, CUDA, LLVM, Python, bash, gdb, git, hg, and vim.

\textbf{I love to} swing dance and teach.

\textbf{I care deeply about} inclusivity.  I was involved with the
\href{https://bloom.bg/2qhgDID}{\textit{Yes, at Google}} project and work on
inclusivity in the swing dance scene.

\section*{Work Samples}

A large fraction of my work these days is helping others (writing and reviewing
designs, reviewing code, etc.), most of which isn't public.  Here's what I can
show:

\begin{itemize}
  \item My \href{https://youtu.be/KHa-OSrZPGo}{CppCon 2016 talk} about GPUs and
    CUDA support in clang
  \item I have some old stuff on my \href{https://jlebar.com}{blog}.  The post
    on rvalue references is a good example of my approach to teaching \Cpp.
  \item Recent \href{https://reviews.llvm.org/D149893}{patch} to rewrite an
    LLVM pass.  This helps with int8 kernels generated by XLA.
  \item
    \href{https://github.com/tensorflow/tensorflow/commit/9cfee581d2ce958d45f798d8a7be7f7e6dde1d41}{Patch}
    adding support for ahead-of-time cudnn/cublas autotuning.  This is a big
    startup-time win for Waymo, plus it makes us more deterministic.  There's a
    whole infrastructure at Waymo to generate these AoT autotuning choices,
    which I designed but didn't implement myself.
  \item
    \href{https://github.com/tensorflow/tensorflow/commit/852afbdcc087ba514ad285c658ff7b2a611d8e67}{``Fun''}
    optimization to XLA:GPU compile time.  This was part of a long chain of
    compile-time optimizations.
\end{itemize}

All my commits to XLA, clang, and LLVM are open-source; Google doesn't maintain
an internal branch.  My github \href{https://github.com/jlebar}{activity
tracker} isn't showing most of my contributions for some reason, so the best I
have to offer is running \texttt{git log} over the repos:
\begin{verbatim}
  $ git clone https://github.com/tensorflow/tensorflow.git
  $ git -C tensorflow --author lebar

  $ git clone https://github.com/llvm/llvm-project.git
  $ git -C llvm-project --author lebar
\end{verbatim}

\end{document}
